Irt plot extra

### 2022-03-30 manuscript.Rmd
Typo corrected in the discussion

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `). However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings. Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance . This item-pair was capturing smart-watch based light exposure behaviour. In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items. Thus, we decided to accept the modification to our model. The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`). On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" holds the true across native and non-native English speakers. This indicates the applicability of LEBA on both native and non-native English Speakers. However, this brings up another question to be answered, what is the required grade level to understand the items of our scale? To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method. Our scale is will appear understandable to those who are at least a grade four student and have a age of at least 8.33 years. As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic]. "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI. However, the aim of those scale and ours was different. Items in those two scales were looking into behaviours related to sleep whereas our  aim was to capture light exposure related behaviour.

>>>>

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `). However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings. Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance . This item-pair was capturing smart-watch based light exposure behaviour. In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items. Thus, we decided to accept the modification to our model. The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`). On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers. This indicated the applicability of LEBA on both native and non-native English Speakers. However, this decisions brought up another question to be answered, what was the required grade level to understand the items of our scale? To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method. Our scale would appear understandable to those who were at least a grade four student and had a age of at least 8.33 years. As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic]. "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI. However, the aim of those scale and ours were different. Items in those two scales were looking into behaviours related to sleep whereas our aim was to capture light exposure related behaviour.
